### 2024-06-27 conteudo/background/codeduplication.tex
Add initial research methods, 27/06

@@

Given the necessity to evaluate and compare approches for code clone detection, it was developed and widely-adopted two datasets: 
OJ-Clone, a dataset collected from a pedagogical online judge system \citep{ojclone}, and BigCloneBench, a datatset collected from over 
25,000 Java software systems \citep{bigclonebench}. The existence of only two spreaded datasets is a open concern in literature as 
the limited scope of OJ-Clone and the problems of BigCloneBench presented by Krinke and Ragkhitwetsagul \citep{bigfail}

@@

>>>>

\label{subsec:types}

@@

@@

\subsection{Methodology to evaluate code duplication methods}

\label{subsec:codumethods}

Given the necessity to evaluate and compare approches for code clone detection, it was developed and widely-adopted two datasets: 
OJ-Clone, a dataset collected from a pedagogical online judge system \citep{ojclone}, and BigCloneBench, a dataset collected from over 
25,000 Java software systems \citep{bigclonebench}. The existence of only two spreaded datasets is a open concern in literature as 
the limited scope of OJ-Clone and the problems of BigCloneBench presented by Krinke and Ragkhitwetsagul \citep{bigfail}

(ADD INFORMATION ABOUT THE MORE SEPARATION OF CLONE TYPES THE BIGCLONEBENCH makes)

### 2024-06-27 conteudo/background/nlpsimilarity.tex
add initial tool, 13/06
Add initial research methods, 27/06

\section{Text similarity detection methods}

@@

Where $A$ and $B$ are the vector embeddings of the two texts. One of the advantages of the cosine similarity is that $SC(A,B)$ 
is a number between $0$ and $1$, where $SC(A,B)$ values more close to the number $1$ means that two vectors are more similar.

>>>>

\section{Text similarity detection methods}
\label{sec:similarity}.

@@

Where $A$ and $B$ are the vector embeddings of the two texts. One of the advantages of the cosine similarity is that $SC(A,B)$ 
is a number between $0$ and $1$, where $SC(A,B)$ values more close to the number $1$ means that two vectors are more similar,
it is common to compare the cosine similarity to aproximation to a probability value, transforming the values between $0$ and $1$ to a
porcentage between $0 \% $ and $100\%$, through our research we will use the porcentage form.

### 2024-06-27 conteudo/introduction/intro.tex
Add initial research methods, 27/06

The code duplication problem outlined in Section \ref{sec:problem} cannot be resolved by the solutions presented in the formal 
literature nor the gray literature, we intend to propose an approach to indentify and mitigate the code duplications in the 
Linux Kernel. For that, we propose a tool capable to indentify code duplications in the kernel, and we mitigate code duplications in the kernel. 
On this research, we expect to extract patterns of software engineers techniques, such as refactoring methods, which we commonly 
used to mitigate the code duplications, thus, serving as guidance to future contributors to approach the code duplications problem 
in the given context. To properly investigate our proposed approach, we developed the research questions below to guie our research.

\textbf{RQ1:} How effective is our approach in mitigating duplicate code in the Linux kernel?

\textbf{RQ1:} How effective is our approach in identifying duplicate code in the Linux kernel?

>>>>

The code duplication problem outlined in Section \ref{sec:problem} cannot be resolved by the solutions presented in the formal 
literature nor the gray literature, we intend to propose an approach to indentify and mitigate the code duplications in the 
Linux Kernel. For that, we propose a tool capable to indentify duplicated functions in the kernel, and we intend to mitigate 
code duplications in the kernel. On this research, we expect to extract patterns of software engineers techniques, 
such as refactoring methods, which we commonly used to mitigate the code duplications, thus, serving as guidance to future 
contributors to approach the code duplications problem in the given context. To properly investigate our proposed approach, 
we developed our primarily research question below to guide our research.

\textbf{RQ1:} How effective is our approach in itendifying and mitigating duplicate code in the Linux kernel?

Given the complexity of the proposed question, we created a supplementary research question, with the objective to verify midway 
results, which is related to the performance of our proposed tool in the Linux kernel, the supplementary research question
is defined as:

\textbf{RQ1.1:} How accurate is the proposed tool for detecting duplicate functions?
